Figures

### 2019-10-02 figures/07_model-selection.Rmd
adjust response labels

```{r re_global}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global          <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term     <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 6), rep("tn", 6))
re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
  dplyr::select(pretty, `5%`:`95%`, term, response)
# re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
# group_by(re_global, response) %>%
#   arrange(desc(`50%`))
```

```{r tp_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x $formula) 
# re_brms[[6]]$formula
best_tp        <- 6 # 6 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

>>>>

```{r re_global}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global          <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term     <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 7), rep("tn", 7))
re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
  dplyr::select(pretty, `5%`:`95%`, term, response)
# re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
# group_by(re_global, response) %>%
#   arrange(desc(`50%`))
```

```{r tp_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x$R2)
# lapply(re_brms, function(x) x $formula) 
# re_brms[[6]]$formula
best_tp        <- 6 # 6 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
